Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-04-27 Paper Sigatoka - 2015.tex
Finalmente pude activar el formato autor agno
Text of introduction reviewed.  Some formulations changed

\documentclass[review]{elsarticle}
\bibliographystyle{elsarticle-harv}

@@

\usepackage{soul}
\usepackage{marginnote}
\usepackage{float}
\usepackage{natbib}
\usepackage{hyperref}

@@

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}

%% APA style
% \bibliographystyle{model5-names}\biboptions{authoryear}

%%%%%%%%%%%%%%%%%%%%%%%

@@

\marginnote{La bibliografia debe ser autor, año}

@@

This disease attacks the plant leaves producing a rapid deterioration
of the leaf area, affects the growth and productivity of the plants
due to the impairment of their photosinthetic ability, causes a
reduction in the quality of the fruit, and promotes premature
maturation \marginnote{maturation or ripening?} of bunches, which is
the major cause of product losses associated with the black
Sigatoka. \figurename~\ref{fig:diseasestages} shows three stages of
this disease.

Phytopathological studies point out that precipitation, temperature,
relative humidity and wind are the main climatic variables that affect
its development \citep{MarinVargas1995}.

\begin{figure}[h] 
\centering
\begin{tabular}{c@{\;}c@{\;}c}
  \includegraphics[width=.32\linewidth]{Roya_a} &
  \includegraphics[width=.32\linewidth]{Roya_b} &
  \includegraphics[width=.32\linewidth]{Roya_c} \\
  (a) & (b) & (c) 
\end{tabular}
\caption{Examples of three disease stages of the black Sigatoka. (a)~Initial stage. (b)~Intermediate stage, and (c)~Advanced stage.} 
\label{fig:diseasestages} 
\end{figure}

In Costa Rica the control of black Sigatoka makes use of chemical fungicides.
%
Depending on the zone of production and the weather conditions, 45--55
cycles/year of fungicide applications are required to keep this
disease under control and to produce the fruit quality expected in the
international markets.
%
This represent a cost per hectare per year in the range between US\$1600 and
US\$2000; about 0.64--0.80 cents of the production costs for a
18.14\,kg box.
%
Overall, this represents 10\%--12\% of the total production cost.

The past and present rates of disease development can in principle be used
to predict its future behavior and to determine whether
a particular fungicide spray program will be able to effectively and
economically control the disease \citet{ChuangJeger1987}.

There are efforts to apply machine learning methods for
decision-making in agriculture, including the control of crop
diseases. For example, \cite{Camargo2012} present an intelligent
system for the assessment of crop disorders, \cite{Huang2010}
introduce a plant virus identification method based on neural networks
with an evolutionary preprocessing stage, \cite{Kim2014} summarize in
their survey crop pests prediction methods using regression and
machine learning approaches, while \cite{Zhao2013} present an
intelligent agricultural forecasting system based on wireless sensor
networks.

In this work, we compare five machine learning techniques (support
vector regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression)
to predict the development rate of the black Sigatoka disease.

@@

\subsubsection{Elastic-Net regression}
Elastic-Net is a linear regression model trained with $L1$ and $L2$ prior as regularizer. This combination allows for learning a sparse model where few of the weights are non-zero like Lasso, while still maintaining the regularization properties of Ridge  \citep{scikitlearn2011}. The convex combination of $L1$ and $L2$ is controled by using the $l1_ratio$ parameter.

>>>>

\documentclass[review,authoryear,english]{elsarticle}

\usepackage{babel}
\usepackage{natbib}

\bibliographystyle{elsarticle-harv}

@@

\usepackage{soul}
\usepackage{marginnote}
\usepackage{float}

\usepackage[hidelinks]{hyperref}

@@

@@

@@

This disease attacks the plant leaves producing a rapid deterioration
of the leaf area, affects the growth and productivity of the plants
due to the impairment of the photosynthetic process, causes a
reduction in the quality of the fruit, and promotes premature
ripening of bunches, which is
the major cause of product losses associated with the black
Sigatoka. \figurename~\ref{fig:diseasestages} shows three stages of
this disease.

\begin{figure}[ht] 
\centering
\begin{tabular}{c@{\;}c@{\;}c}
  \includegraphics[width=.32\linewidth]{Roya_a} &
  \includegraphics[width=.32\linewidth]{Roya_b} &
  \includegraphics[width=.32\linewidth]{Roya_c} \\
  (a) & (b) & (c) 
\end{tabular}
\caption{Examples of three disease stages of the black Sigatoka. (a)~Initial stage. (b)~Intermediate stage, and (c)~Advanced stage.} 
\label{fig:diseasestages} 
\end{figure}

Phytopathological studies point out that precipitation, temperature,
relative humidity and wind are the main climatic variables that affect
the development of this disease \citep{MarinVargas1995}.

In Costa Rica the black Sigatoka is frequently treated with
chemical fungicides.
%
Depending on the zone of production and the weather conditions,
45--55~cycles/year of fungicide applications are required to keep this
disease under control and to produce the expected fruit quality for the
international markets.
%
This represent a cost per hectare per year in the range between US\$1600 and
US\$2000; about 0.64--0.80 cents of the production costs for a
18.14\,kg box.
%
Overall, this represents 10\%--12\% of the total production costs.

The past and present rates of disease development can in principle be used
to predict its future behavior and to determine whether
a particular fungicide spray program will be able to effectively and
economically control the disease \citep{ChuangJeger1987}.

There are efforts to apply machine learning methods to support
decision-making in agriculture, including the control of crop
diseases. For example, \cite{Camargo2012} present an intelligent
system for the assessment of crop disorders, \cite{Huang2010}
introduce a plant virus identification method based on neural networks
with an evolutionary preprocessing stage, \cite{Kim2014} summarize in
their survey crop pests prediction methods using regression and
machine learning approaches, while \cite{Zhao2013} present an
intelligent agricultural forecasting system based on wireless sensor
networks.

In this work, we compare five machine learning techniques 
to predict the development rate of the black Sigatoka disease:
support
vector regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression.

@@

\subsubsection{Elastic-Net regression}
Elastic-Net is a linear regression model trained with $L1$ and $L2$ prior as regularizer. This combination allows for learning a sparse model where few of the weights are non-zero like Lasso, while still maintaining the regularization properties of Ridge  \citep{scikitlearn2011}. The convex combination of $L1$ and $L2$ is controled by using the $l1_{ratio}$ parameter.
